---
title: "Feedback"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,     # don't show code chunks
  message = FALSE,  # don't show code messages
  warning = FALSE,  # don't show code warnings
  out.width = "75%" # show images at 75% page width
)
library(markr)
```

```{r, eval=F}
# set eval=T to knit this example for debugging
marks <- demo_marks  # load your data as 
id <- marks[1, ]    # selects just the first row
```

## Research Summary Report for `r id$name`

### General Information

This is a basic summary report of the three behaviors we observed in the laboratory experiment which you took part on `r id$date`.

Note that week collected information on the following areas: passiveness, aggression, and disinterest. These were coded by research assistants and the mentoring professor.

### Passiveness Behaviors

After observation, your passiveness was rated as **`r id$bx1`**. The possible range of these scores was 1 to 5. 

### Aggresssion Behaviors

After observation, your aggression was rated as **`r id$bx2`**. The possible range of these scores was 1 to 7.

### Disinterest

After observation, your disinterest was rated as **`r id$bx3`**. The possible range of these scores was 1 to 10.

### Additional Comments

These are comments from the behavior coders, as approved by the mentoring professor:

`r id$comments`
